Self Regulation Ontology Retest Data Report

### 2018-01-20 code/SRO_Report.Rmd
checking new release

```{r}
test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/demographic_health.csv')

retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/demographic_health.csv')

@@

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables.csv')
tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_noDDM.csv')
tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_EZ.csv')
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

### Load time 1 data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')

@@

```{r}
test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')

@@

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/variables_exhaustive.csv')

@@

```{r}
hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')

>>>>

```{r}
test_demog <- read.csv(paste0(retest_data_path, '/t1_data/demographic_health.csv'))

retest_demog <- read.csv(paste0(retest_data_path, 'demographic_health.csv'))

@@

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv(paste0(test_data_path,'meaningful_variables.csv'))
tmp2 <- read.csv(paste0(test_data_path,'meaningful_variables_noDDM.csv'))
tmp3 <- read.csv(paste0(test_data_path,'meaningful_variables_EZ.csv'))
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

### Load time 1 data
```{r}
test_data <- read.csv(paste0(retest_data_path,'t1_data/variables_exhaustive.csv'))

@@

```{r}
test_data2 <- read.csv(paste0(retest_data_path, 't1_data/variables_exhaustive.csv'))

@@

### Load time 2 data 
```{r}
retest_data <- read.csv(paste0(retest_data_path,'variables_exhaustive.csv'))

@@

```{r}
hddm_refits <- read.csv(paste'/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
